RTS AI: Problems and Techniques

### 2015-01-11 ECGG_RTSProblems/ECGG_RTSProblems.tex
Tightened up some explanations, reduced to 15 pages, and added conclusions

\begin{abstract}
  This is the abstract.
\end{abstract}

\section{Introduction}\label{sec:intro}
The  field of  Real-Time Strategy  (RTS) game  Artificial Intelligence
(AI) has advanced significantly since Michael Buro's call for research
in this area \cite{Buro03rts}. Specially, competitions like the ``ORTS
RTS  Game AI  Competition''  (held  from 2006  to  2009), the  ``AIIDE
StarCraft AI Competition'' (held since  2010), and the ``CIG StarCraft
RTS AI Competition'' (held since  2011) have motivated the exploration
of many AI approaches  in the  context of  RTS AI. This paper, based on the work work presented in \cite{ontanon2013survey}, lists the open problems in RTS game AI, and the approaches that have been proposed to address these problems.

Complex  dynamic  environments,  where neither  perfect  nor  complete
information  about the  current state  or  about the  dynamics of  the
environment are available, pose  significant challenges for artificial
intelligence. Road traffic, finance, or weather forecasts are examples
of such large, complex, real-life  dynamic environments. RTS games can
be seen  as a simplification  of one such real-life  environments, with
simpler dynamics in a finite and smaller world, although still complex
enough to  study some  of the key  interesting problems  like decision
making under  uncertainty or  real-time adversarial  planning. Finding
efficient techniques for tackling these problems on RTS games can thus
benefit other  AI disciplines and  application domains, and  also have
concrete and direct applications in the ever growing industry of video
games.

@@

Real-Time Strategy is a sub-genre of strategy games where players need
to  build an  economy (gathering  resources and  building a  base) and
military power (training units  and researching technologies) in order
to defeat  their opponents  (destroying their army  and base).  From a
theoretical point of view, the  main differences between RTS games and
traditional board games such as Chess are:

\begin{itemize}
\item  RTS games are  {\em simultaneous  move} games,  where more  than one
  player  can issue  actions  at the  same  time. 
\item Action in RTS games are {\em durative}, i.e.  actions are not instantaneous, but
  take some amount of time to complete.
\item RTS games  are ``real-time'', which actually means  is that each
  player  has  a  very  small  amount  of  time  to  decide  the  next
  move. Compared to  Chess, where players may have  several minutes to
  decide the next action, in StarCraft, a popular RTS game, the game executes at 24 frames
  per second, which means that players  can act as fast as every 42ms,
  before the game state changes.
\item Most  RTS games are  partially observable: players can  only see
  the part of the  map that has been explored. This  is referred to as
  the {\em fog-of-war}.
\item Most RTS games are non-deterministic: some actions have a chance
  of success, and the amount of damage dealt by different units is sometimes stochastic.
\item And  finally, the complexity  of these  games, both in  terms of
  state space size and in terms of number of actions available at each
  decision cycle is very large. For  example, the state space of Chess
  is typically  estimated to  be around  $10^{50}$, heads  up no-limit
  Texas holdem  poker around $10^{80}$,  and Go around  $10^{170}$. In
  comparison,  the  state space  of  StarCraft  in  a typical  map  is
  estimated to be  many orders of magnitude larger than  any of those,
  as discussed in the next section.
\end{itemize}

@@

From a theoretical point of view,  the state space of a StarCraft game
for a  given map is  enormous.  For  example, consider a  typical $128
\times 128$ map. At any given moment  there might be between 50 to 400
units in  the map, each of  which might have a  complex internal state
(remaining energy  and hit-points, action being  executed, etc.). This
quickly leads to an immense number  of possible states (way beyond the
size  of smaller  games,  such  as Chess  or  Go).  For example,  just
considering the location of each  unit (with $128 \times 128$ possible
positions per  unit), and  400 units,  gives us  an initial  number of
$16384^{400} \approx 10^{1685}$. If we add the other factors playing a
role in the game, we obtain even larger numbers (see \ref{ontanon2013survey} for a more in-depth description of the complexity of StarCraft).

@@

% From Gabriel's dissertation:
% ------------------------------------
%How does the state of possible actions grow? To measure this, we
%used a measure from perfect information zero-sum games (as Checkers,
%Chess and Go): the branching factor* b and the depth d of a typical
%game. The complexity of a game (for taking a decision) is proportional
%to bd.
%[...]
%In RTS games, b = 200 is a lower bound (in StarCraft we may have
%between 50 to 400 units to control), and very good amateurs and
%professional players perform more than 300 actions per minute. As
%StarCraft is a simultaneous move, multi-units game, a strict number
%for b would be |actions||units| (actions account for atomic moves and
%abilities), thus for StarCraft b would be around 30^{60}. Strictly
%speaking, for a StarCraft game, d = 24  game_seconds (24 game frames
%per second), with a game duration of 25 minutes, this gives d =
%36,000, thus b^d Å 30^{60^{36000}} .

\subsection{Challenges in RTS Game AI}\label{subsec:challenges}

Early research  in AI  for RTS  games \cite{Buro03rts}  identified the
following six challenges:
\begin{itemize}
\item Resource management
\item Decision making under uncertainty
\item Spatial and temporal reasoning
\item Collaboration (between multiple AIs)
\item Opponent modeling and learning
\item Adversarial real-time planning
\end{itemize}

While there  has been  a significant  work in  many, others  have been
untouched (e.g. collaboration). Moreover, recent research in this area
has identified several additional research  challenges, such as how to
exploit the massive amounts  of existing domain knowledge (strategies,
build-orders,  replays,  and  so   on).  Below,  we  describe  current
challenges in RTS Game AI, grouped in six main different areas.

@@

\subsubsection{Learning}
Given  the  difficulties  in  playing  RTS  games  by  directly  using
adversarial  planning techniques,  many  research  groups have  turned
attention to  learning techniques. We  can distinguish three  types of
learning problems in RTS games:
\begin{itemize}
\item {\em Prior learning}: How can we exploit available data, such as
  existing replays,  or information  about specific maps  for learning
  appropriate strategies before hand? A significant amount of work has
  gone in this
  direction.%, such as \cite{WeberCIG09,SynnaeveCIG11,SynnaeveAIIDE11,OntanonMSR10}.
\item  {\em In-game  learning}: How  can bots  deploy online  learning
  techniques that allow them to  improve their game play while playing
  a  game?  These  techniques  might  include  reinforcement  learning
  techniques, but  also opponent modeling.  The main problem  again is
  the fact  that the state  space is too large  and the fact  that RTS
  games are partially observable.
\item {\em  Inter-game learning}:  What can be  learned from  one game
  that can  be used  to increase  the chances of  victory in  the next
  game? Some work has used simple game-theoretical solutions to select
  amongst a  pool of  predefined strategies,  but the  general problem
  remains unsolved.
\end{itemize}

@@

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial reasoning is  related to each aspect  of terrain exploitation.
It  is  involved   in  tasks  such  as  building   placement  or  base
expansion.  In the  former,  the player  needs  to carefully  consider
building  positioning into  its  own  bases to  both  protect them  by
creating  a wall  against invasions  and to  avoid bad  configurations
where large units could be stuck. In base expansion, the player has to
choose good available locations to build a new base, regarding its own
position and  opponent's bases. Finally,  spatial reasoning is  key to
tactical reasoning:  players need to  decide where to place  units for
battle, favoring, for instance,  engagements when the opponent's units
are lead into a bottleneck.

@@

% [Alberto: I  guess Weber's number comes  from StarCraft walkthroughs
% like                                                           this:
% http://www.supercheats.com/pc/walkthroughs/starcraftbroodwar-walkthrough01.txt,
% there is also a chance to hit in even grounds (like
% 98%). But since we cannot see the original code all of these numbers are approximations. In any case we can keep explaining the concept without numbers ;)]
Another example of spatial reasoning in StarCraft is that it is always
an advantage to  have own units on  high ground while the  enemy is on
low ground,  since units on  low ground have  no vision onto  the high
ground. %, and firing from low ground have a chance to hit units on high ground.
%MP: took out last half sentence as it seems to be rather confusing.

@@

\subsubsection{Domain Knowledge Exploitation}
In traditional board  games such as Chess,  researchers have exploited
the  large  amounts  of  existing  domain  knowledge  to  create  good
evaluation  functions  to be  used  by  alpha-beta search  algorithms,
extensive opening books, or end-game tables. In the case of RTS games,
it  is still  unclear how  the  significantly large  amount of  domain
knowledge  (in the  forms or  strategy guides,  replays, etc.)  can be
exploited by  bots. Most  work in  this area has  focused on  two main
directions: on the one hand, researchers  are finding ways in which to
hard-code existing  strategies into  bots, so that  bots only  need to
decide  which strategies  to deploy,  instead of  having to  solve the
complete  problem  of  deciding  which  actions  to  execute  by  each
individual unit at each time step.  One the other hand, large datasets
of  replays have  been created  \cite{WeberCig09,synnaeve2012dataset},
from  where   strategies,  trends   or  plans   have  been   tried  to
learn.  However,  StarCraft  games  are  quite  complex,  and  how  to
automatically learn from such datasets is still an open problem.

\subsubsection{Task Decomposition}
For all the  previous reasons, most existing approaches  to play games
as StarCraft  work by decomposing the  problem of playing an  RTS game
into   a    collection   of    smaller   problems,   to    be   solved
independently. Specifically, a common subdivision is:
\begin{itemize}
\item {\em  Strategy}: corresponds  to the high-level  decision making
  process.  This is  the highest  level  of abstraction  for the  game
  comprehension.  Finding an  efficient  strategy or  counter-strategy
  against a given opponent is key in RTS games, and concerns the whole
  set of units a player
  owns. %If we may allow ourselves a military analogy, strategy is orders given by generals at the HQ.
\item   {\em  Tactics}:   are  the   implementation  of   the  current
  strategy.  It  implies  army and  building  positioning,  movements,
  timing, and so on. Tactics concerns a group of
  units. %They are orders given by officers on the battlefield.
\item {\em Reactive  control}: is the implementation  of tactics. This
  consists   in  moving,   targeting,  firing,   fleeing,  hit-and-run
  techniques  (also  knows  as  ``kiting'')  during  battle.  Reactive
  control focuses on a specific
  unit. %It is soldiers applying officers' orders.
%\end{itemize}
%
%\noindent
%Both  strategy  and  tactics  are  usually  called
%\textit{macro-management}, whereas reactive control is also called
%\textit{micro-management}. In addition of the three tasks shown above,
%one could also consider these two tasks that an AI has to deal with:
%\begin{itemize}
\item  {\em Terrain  analysis}: consists  in the  analysis of  regions
  composing the map: choke-points,  minerals and gas emplacements, low
  and high walkable grounds, islands, etc.
\item  {\em   Intelligence  gathering}:  corresponds   to  information
  collected  about the  opponent. Because  of the  fog-of-war, players
  must regularly send scouts to localize and spy enemy
  bases.%, and must see or infer what buildings and technology the enemy has developed in order to adapt its strategy.
\end{itemize}

@@

The reader can find a good  presentation of task decomposition for AIs
playing  RTS   in~\cite{weber2011acs}.  Although  the   previous  task
decomposition  is  common, a  significant  challenge  is on  designing
architectures so that  the individual AI techniques  that address each
of  those  tasks  can   communicate  and  effectively  work  together,
resolving conflicts, or prioritizing resources between them.% Section
%\ref{sec:bot}  provides an  overview of  the task  decompositions that
%state-of-the-art bots use.  
Moreover, we would like to  point out that
the task decomposition  above is not the only  possible approach. Some
systems, such  as IMAI  \cite{miles2007co}, divide gameplay  into much
smaller  tasks, which  are then  assigned resources  depending on  the
expected benefits of achieving each task.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{figures/levels_abstraction.pdf}
    \caption{RTS  AI  levels  of abstraction  and  theirs  properties:
      uncertainty  (coming  from  partial  observation  and  from  not
      knowing the  intentions of  the opponent)  is higher  for higher
      abstraction  levels.  Timings  on  the right  correspond  to  an
      estimate   of   the   duration   of   a   behavior   switch   in
      StarCraft. Spatial and temporal  reasoning are indicated for the
      levels at which greedy solutions are not enough.}
    \label{fig:levels-abstraction}
\end{figure}

@@

Following this idea, we consider  strategy to be everything related to
the  technology trees,  build-order\footnote{The {\em  build-order} is
  the specific sequence in which  buildings of different types will be
  constructed at  the beginning of  a game, and  completely determines
  the   long-term  strategy   of  a   player.},  upgrades,   and  army
composition. It  is the most  deliberative level, as a  player selects
and performs  a strategy  with future stances  (aggressive, defensive,
economy, technology)  and tactics in  mind. We consider tactics  to be
everything related to confrontations between groups of units. Tactical
reasoning involves both spatial  (exploiting the terrain) and temporal
(army  movements)  reasoning, constrained  on  the  possible types  of
attacks   by  the   army   composition  of   the   player  and   their
opponent. Finally, reactive control  describes how the player controls
individual units to  maximize their efficiency in  real-time. The main
difference  between  tactics and  reactive  control  is that  tactical
reasoning  typically involves  some sort  of planning  ahead for  some
short spans  of time,  whereas reactive  control involves  no planning
ahead whatsoever.

% Example:
For example,  after starting a  game, a player  might decide to  use a
{\em rushing}  strategy (which involves  quickly building an  army and
sending it  to attack as  early as possible  in the game);  then, when
performing the attack use a {\em surrounding} tactic, where the player
tries to surround the enemy  cutting potential escape routes; finally,
while executing the surrounding tactic, the player might decide to use
reactive control  techniques that command individual  units to perform
repeated {\em attack  and flee} movements, to  maximize the efficiency
of each of the units being used in the attack.

@@

% INTRO:
Strategic  decision  making in  real-time  domains  is still  an  open
problem. In the context of RTS  games is has been addressed using many
AI techniques, like  hard-coded approaches, planning-based approaches,
or  machine   learning-based  approaches.  We  cover   each  of  these
approaches in turn.

@@

% SCOUTING:
\subsubsection{Scouting}
Additionally,  scouting  is  equally important  in  tactical  decision
making as in strategic decision making. However, as mentioned earlier,
very little work has been done in this respect, being that of Weber et
al. \cite{WeberAIIDE11}  the only exception. All  previous approaches,
including all game tree search ones, assume complete information.

@@

Reactive control %, also called micro-management in RTS games,
aims at maximizing the  effectiveness of units, including simultaneous
control  of   units  of   different  types   in  complex   battles  on
heterogeneous terrain.

@@

%\section{Conclusions}
%
%This paper has summarized the set of open problem in RTS game AI, and summarized existing work toward addressing those problems.

>>>>

%\begin{abstract}
%  This is the abstract.
%\end{abstract}

\section{Introduction}\label{sec:intro}
The  field of  Real-Time Strategy  (RTS) game  Artificial Intelligence
(AI) has advanced significantly in the past few year, partially thanks to competitions like the ``ORTS
RTS  Game AI  Competition''  (held  from 2006  to  2009), the  ``AIIDE
StarCraft AI Competition'' (held since  2010), and the ``CIG StarCraft
RTS AI Competition'' (held since  2011). Based on the work work presented in \cite{ontanon2013survey}, here we first define RTS games, and then list here the open problems in creating AI for RTS games, and the approaches that have been proposed to address these problems.

%Complex  dynamic  environments,  where neither  perfect  nor  complete
%information  about the  current state  or  about the  dynamics of  the
%environment are available, pose  significant challenges for artificial
%intelligence. Road traffic, finance, or weather forecasts are examples
%of such large, complex, real-life  dynamic environments. RTS games can
%be seen  as a simplification  of one such real-life  environments, with
%simpler dynamics in a finite and smaller world, although still complex
%enough to  study some  of the key  interesting problems  like decision
%making under  uncertainty or  real-time adversarial  planning. Finding
%efficient techniques for tackling these problems on RTS games can thus
%benefit other  AI disciplines and  application domains, and  also have
%concrete and direct applications in the ever growing industry of video
%games.

@@

{\em Real-Time Strategy} (RTS) is a sub-genre of strategy games where players need
to  build an  economy (gathering  resources and  building a  base) and
military power (training units  and researching technologies) in order
to defeat  their opponents  (destroying their army  and base).  From a
theoretical point of view, the  main differences between RTS games and
traditional board games such as Chess are:

\begin{itemize}
\item  RTS games are  {\em simultaneous  move} games,  where more than one
  player  can issue  actions  at the  same  time. 
\item Action in RTS games are {\em durative}, i.e.  actions are not instantaneous, but
  take some amount of time to complete.
\item RTS games  are ``real-time'', which actually means is that each
  player  has  a  very  small  amount  of  time  to  decide  the  next
  move, and that, in contrast to {\em turn-based} games, the game keeps advancing even if a player does not execute any actions. Compared to  Chess, where players may have several minutes to
  decide the next action, in StarCraft, a popular RTS game, the game executes at 24 frames
  per second, which means that players  can act as fast as every 42ms,
  before the game state changes.
\item Most  RTS games are  partially observable: players can  only see
  the part of the  map that has been explored. This  is referred to as
  the {\em fog-of-war}.
\item Most RTS games are non-deterministic: some actions have a chance
  of success, and the amount of damage dealt by different units is sometimes stochastic.
\item And  finally, the complexity  of these  games, both in  terms of
  state space size and in terms of number of actions available at each
  decision cycle is very large. For  example, the state space of Chess
  is typically  estimated to  be around  $10^{50}$, heads  up no-limit
  Texas holdem  poker around $10^{80}$,  and Go around  $10^{170}$. In
  comparison,  the  state space  of  StarCraft  in  a typical  map  is
  estimated to be  many orders of magnitude larger than  any of those,
  as discussed in the next section.
\end{itemize}

@@

From a theoretical point of view,  the state space of a StarCraft game
for a  given map is  enormous.  For  example, consider a  typical $128
\times 128$ map. At any given moment  there might be between 50 to 400
units in  the map, each of  which might have a  complex internal state
(remaining energy  and hit-points, action being  executed, etc.). This
quickly leads to an immense number  of possible states (way beyond the
size  of smaller  games,  such  as Chess  or  Go).  For example,  just
considering the location of each  unit (with $128 \times 128$ possible
positions per  unit), and  400 units,  gives us  an initial  number of
$16384^{400} \approx 10^{1685}$. If we add the other factors playing a
role in the game, such as resources, hit-points, energy, research status, cool-down timers, etc., we obtain even larger numbers (see \cite{ontanon2013survey} for a more in-depth description of the complexity of StarCraft).

@@

% From Gabriel's dissertation:
% ------------------------------------
%How does the state of possible actions grow? To measure this, we
%used a measure from perfect information zero-sum games (as Checkers,
%Chess and Go): the branching factor* b and the depth d of a typical
%game. The complexity of a game (for taking a decision) is proportional
%to bd.
%[...]
%In RTS games, b = 200 is a lower bound (in StarCraft we may have
%between 50 to 400 units to control), and very good amateurs and
%professional players perform more than 300 actions per minute. As
%StarCraft is a simultaneous move, multi-units game, a strict number
%for b would be |actions||units| (actions account for atomic moves and
%abilities), thus for StarCraft b would be around 30^{60}. Strictly
%speaking, for a StarCraft game, d = 24  game_seconds (24 game frames
%per second), with a game duration of 25 minutes, this gives d =
%36,000, thus b^d Å% 30^{60^{36000}} .
%I

\section{Challenges in RTS Game AI}\label{subsec:challenges}

Early research  in AI  for RTS  games \cite{Buro03rts}  identified the
following six challenges: Resource management, Decision making under uncertainty, Spatial and temporal reasoning, Collaboration (between multiple AIs), Opponent modeling and learning, and Adversarial real-time planning. While there  has been  a significant  work in  many, others  have been
untouched (e.g. collaboration). Moreover, recent research in this area
has identified several additional research  challenges, such as how to
exploit the massive amounts  of existing domain knowledge (strategies,
build-orders,  replays,  and  so   on). Thus, the challenges in RTS game AI can be grouped in six main different areas, described below.

@@

\subsubsection{Learning}
Given  the  difficulties  in  playing  by  directly  using
adversarial  planning techniques,  many  research  groups have  turned
attention to  learning techniques. We  can distinguish three  types of
learning problems in RTS games:
\begin{itemize}
\item {\em Prior learning}: How can we exploit available data, such as
  existing replays,  or information  about specific maps  for learning
  appropriate strategies before hand? A significant amount of work has
  gone in this
  direction.%, such as \cite{WeberCIG09,SynnaeveCIG11,SynnaeveAIIDE11,OntanonMSR10}.
\item  {\em In-game  learning}: How  can bots  deploy online  learning
  techniques that allow them to  improve their game play while playing
  a  game?  These  techniques  might  include  reinforcement  learning
  techniques, but  also opponent modeling.  The main problem  again is
  the fact  that the state  space is too large  and the fact  that RTS
  games are partially observable.
\item {\em  Inter-game learning}:  What can be  learned from  one game
  that can  be used  to increase  the chances of  victory in  the next
  game? Some work has used simple game-theoretical solutions to select
  amongst a  pool of  predefined strategies,  but the  general problem
  remains unsolved.
\end{itemize}

@@

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial reasoning is  related to each aspect  of terrain exploitation.
It  is  involved   in  tasks  such  as  building   placement  or  base
expansion.  In the  former,  the player  needs  to carefully  consider
building  positioning into  its  own  bases to  both  protect them  by
creating  defenses or walls  against invasions  and to  avoid bad  configurations
where large units could be stuck. In base expansion, the player has to
choose good available locations to build a new base, regarding its own
position and  opponent's bases. Finally,  spatial reasoning is  key to
tactical reasoning:  players need to  decide where to place  units for
battle, favoring, for instance,  engagements when the opponent's units
are lead into a bottleneck.

@@

% [Alberto: I  guess Weber's number comes  from StarCraft walkthroughs
% like                                                           this:
% http://www.supercheats.com/pc/walkthroughs/starcraftbroodwar-walkthrough01.txt,
% there is also a chance to hit in even grounds (like
% 98%). But since we cannot see the original code all of these numbers are approximations. In any case we can keep explaining the concept without numbers ;)]
%Another example of spatial reasoning in StarCraft is that it is always
%an advantage to  have own units on  high ground while the  enemy is on
%low ground,  since units on  low ground have  no vision onto  the high
%ground. %, and firing from low ground have a chance to hit units on high ground.
%MP: took out last half sentence as it seems to be rather confusing.

@@

\subsubsection{Domain Knowledge Exploitation}
In traditional board  games such as Chess,  researchers have exploited
the  large  amounts  of  existing  domain  knowledge  to  create  good
evaluation  functions  to be  used  by  alpha-beta search  algorithms,
extensive opening books, or end-game tables. In the case of RTS games,
it  is still  unclear how  the  significantly large  amount of  domain
knowledge  (in the  forms or  strategy guides,  replays, etc.)  can be
exploited. Most  work in  this area has  focused on  two main
directions: (1) hard-coding existing strategies into bots (so that  bots only  need to
decide  which strategies  to deploy,  instead of  having to  solve the
complete  planning problem), and (2) mining large datasets
of  replays \cite{WeberCig09,synnaeve2012dataset} to automatically extract
 strategies,  trends   or  plans. % However,  StarCraft  games  are  quite  complex,  and  how  to
%automatically learn from such datasets is still an open problem.

\subsubsection{Task Decomposition}
Most existing approaches  to play RTS games work by decomposing the  problem into   a    collection   of    smaller   problems to    be   solved
independently. Specifically, a common subdivision is:
\begin{itemize}
\item {\em  Strategy}: corresponds  to the high-level  decision making
  process.  This is  the highest  level  of abstraction  for the  game
  comprehension.  Finding an  efficient  strategy or  counter-strategy
  against a given opponent is key in RTS games, and concerns the whole
  set of units a player
  owns. %If we may allow ourselves a military analogy, strategy is orders given by generals at the HQ.
\item   {\em  Tactics}:   are  the   implementation  of   the  current
  strategy.  It  implies  army and  building  positioning,  movements,
  timing, and so on. Tactics concerns a group of
  units. %They are orders given by officers on the battlefield.
\item {\em Reactive  control}: is the implementation  of tactics. This
  consists   in  moving,   targeting,  firing,   fleeing,  hit-and-run
  techniques  (also  knows  as  ``kiting'')  during  battle.  Reactive
  control focuses on a specific
  unit. %It is soldiers applying officers' orders.
%\end{itemize}
%
%\noindent
%Both  strategy  and  tactics  are  usually  called
%\textit{macro-management}, whereas reactive control is also called
%\textit{micro-management}. In addition of the three tasks shown above,
%one could also consider these two tasks that an AI has to deal with:
%\begin{itemize}
\item  {\em Terrain  analysis}: consists  in the  analysis of  regions
  composing the map: choke-points,  minerals and gas emplacements, low
  and high walkable grounds, islands, etc.
\item  {\em   Intelligence  gathering}:  corresponds   to  information
  collected  about the  opponent. Because  of the  fog-of-war, players
  must regularly send scouts to localize and spy enemy
  bases.%, and must see or infer what buildings and technology the enemy has developed in order to adapt its strategy.
\end{itemize}

@@

The reader can find a good  presentation of task decomposition RTS game AI in~\cite{weber2011acs}.  Although  the   previous  task decomposition  is  common, other task decompositions have been explored (see \cite{ontanon2013survey} for an overview of the task decomposition used by several StarCraft bots).

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/levels_abstraction.pdf}
    \caption{RTS  AI  levels  of abstraction  and  theirs  properties:
      uncertainty  (coming  from  partial  observation  and  from  not
      knowing the  intentions of  the opponent)  is higher  for higher
      abstraction  levels.  Timings  on  the right  correspond  to  an
      estimate   of   the   duration   of   a   behavior   switch   in
      StarCraft. Spatial and temporal  reasoning are indicated for the
      levels at which greedy solutions are not enough.}
    \label{fig:levels-abstraction}
\end{figure}

@@

The remainder of this section presents work toward addressing the previous six open RTS game AI problems, grouped as work focused toward strategy, tactics, or reactive control, as well as a final section dedicated to holistic approaches that attempt to deal with all three levels at once.

%Following this idea, we consider  strategy to be everything related to
%the  technology trees,  build-order\footnote{The {\em  build-order} is
%  the specific sequence in which  buildings of different types will be
%  constructed at  the beginning of  a game, and  completely determines
%  the   long-term  strategy   of  a   player.},  upgrades,   and  army
%composition. It  is the most  deliberative level, as a  player selects
%and performs  a strategy  with future stances  (aggressive, defensive,
%economy, technology)  and tactics in  mind. We consider tactics  to be
%everything related to confrontations between groups of units. Tactical
%reasoning involves both spatial  (exploiting the terrain) and temporal
%(army  movements)  reasoning, constrained  on  the  possible types  of
%attacks   by  the   army   composition  of   the   player  and   their
%opponent. Finally, reactive control  describes how the player controls
%individual units to  maximize their efficiency in  real-time. The main
%difference  between  tactics and  reactive  control  is that  tactical
%reasoning  typically involves  some sort  of planning  ahead for  some
%short spans  of time,  whereas reactive  control involves  no planning
%ahead whatsoever.

% Example:
%For example,  after starting a  game, a player  might decide to  use a
%{\em rushing}  strategy (which involves  quickly building an  army and
%sending it  to attack as  early as possible  in the game);  then, when
%performing the attack use a {\em surrounding} tactic, where the player
%tries to surround the enemy  cutting potential escape routes; finally,
%while executing the surrounding tactic, the player might decide to use
%reactive control  techniques that command individual  units to perform
%repeated {\em attack  and flee} movements, to  maximize the efficiency
%of each of the units being used in the attack.

@@

% INTRO:
In the context of RTS  games, high-level strategic reasoning has been addressed using many
AI techniques, like  hard-coded approaches, planning,
or  machine   learning.  We  cover   each  of  these
approaches in turn.

@@

%% SCOUTING:
%\subsubsection{Scouting}
%Additionally,  scouting  is  equally important  in  tactical  decision
%making as in strategic decision making. However, as mentioned earlier,
%very little work has been done in this respect, being that of Weber et
%al. \cite{WeberAIIDE11}  the only exception. All  previous approaches,
%including all game tree search ones, assume complete information.

@@

Reactive control has been addressed mainly via the application of potential fields or by using machine learning to learn good control policies. We also include work on path-finding as part of reactive control.

%Reactive control %, also called micro-management in RTS games,
%aims at maximizing the  effectiveness of units, including simultaneous
%control  of   units  of   different  types   in  complex   battles  on
%heterogeneous terrain.

@@

\section{Conclusions}

This entry has defined real-time strategy (RTS) games from an AI point of view, and summarized the set of open problems in RTS game AI. After that, we have summarized existing work toward addressing those problems.

RTS games can be seen as a simulation of real complex dynamic environments, in a finite and smaller world, but still complex enough to study a series of key interesting problems. Finding efficient techniques for tackling these problems on RTS games can thus benefit other  AI disciplines and  application domains, and  also have concrete and direct applications in the ever growing industry of video games.
